\documentclass[11pt]{letter}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}

\date{25 May 2026}
\signature{Aditrivaishnavi Balaji \\ Parker T.\ Johnson}

\address{Aditrivaishnavi Balaji \\
BASIS Independent Silicon Valley \\
1290 Parkmoor Ave, San Jose, CA \\[6pt]
Parker T.\ Johnson \\
Steward Observatory \\
The University of Arizona \\
933 North Cherry Avenue, Tucson, AZ}

\begin{document}

\begin{letter}{The Editorial Office \\
Monthly Notices of the Royal Astronomical Society}

\opening{Dear Editor,}

We submit the enclosed manuscript, ``A morphological barrier: quantifying
the injection realism gap for CNN strong lens finders in DESI Legacy
Survey DR10,'' for consideration as a Paper in MNRAS.

This manuscript has not been published previously and is not under
consideration by any other journal.  All authors have read the final
version and approved its submission.

\medskip
\noindent\textbf{AI tool disclosure.}
Per MNRAS policy, we note that AI language models (Claude, Anthropic;
ChatGPT, OpenAI) were used as coding assistants during the development
of analysis scripts and for manuscript copy-editing.  All AI-assisted
code was reviewed, tested, and verified by the authors, who are solely
responsible for the scientific content of this paper.

\medskip
We have no preferred or non-preferred editors or reviewers.

\medskip
\noindent The authors declare no conflicts of interest.

\bigskip
\noindent Yours sincerely,\\[6pt]
Aditrivaishnavi Balaji\\
Parker T.\ Johnson

\end{letter}
\end{document}
