\documentclass[11pt]{letter}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}

\date{21 June 2026}
\signature{Aditrivaishnavi Balaji \\ Parker T.\ Johnson}

\address{Aditrivaishnavi Balaji \\
BASIS Independent Silicon Valley \\
1290 Parkmoor Ave, San Jose, CA \\[6pt]
Parker T.\ Johnson \\
Steward Observatory \\
The University of Arizona \\
933 North Cherry Avenue, Tucson, AZ}

\begin{document}

\begin{letter}{The Editorial Office \\
RAS Techniques and Instruments}

\opening{Dear Editor,}

We submit our manuscript, ``A morphological barrier: quantifying the
injection realism gap for CNN strong lens finders in DESI Legacy Survey
DR10,'' for consideration as a Research article in RAS Techniques and
Instruments.

This manuscript was originally submitted to MNRAS (MN-26-1590-P). The
MNRAS Editorial Board judged it a methods contribution that falls outside
the scope of MNRAS and recommended transfer to RASTI, which we have
accepted. As a study of machine-learning methods, data-analysis
techniques, and openly released software for calibrating convolutional
neural network lens finders, we believe it falls squarely within RASTI's
scope.

The injection-recovery pipeline, the selection-function grid results, and
the analysis code accompanying this paper are publicly available in a
GitHub repository to support reuse by the community; details are given in
the Data Availability statement.

This manuscript has not been published previously and is not under
consideration by any other journal. All authors have read the final
version and approved its submission.

\medskip
\noindent\textbf{AI tool disclosure.}
In accordance with RASTI policy, we disclose that AI language models
(Claude, Anthropic; ChatGPT, OpenAI) were used as coding assistants
during the development of analysis scripts and for manuscript
copy-editing. All AI-assisted code was reviewed, tested, and verified by
the authors, who are solely responsible for the scientific content of
this paper.

\medskip
We have no preferred or non-preferred reviewers.

\medskip
\noindent Authors declare no conflict of interest.

\bigskip
\noindent Yours sincerely,\\[6pt]
Aditrivaishnavi Balaji\\
Parker T.\ Johnson

\end{letter}
\end{document}
